### 2022-08-26 Bloods Data Sheet.Rmd
added cleaned data sheet and plots

@@

>>>>

```{r}
main_df2 <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Main_Data_Frame (Outliers_Removed).csv")
```

@@

```{r}
main_df2 <- main_df2%>%
  #filter(!Sample %in% 22)%>%
  filter(!Sample %in% 235)%>%
  filter(!Sample %in% 236)%>%
  mutate(Dilution_Factor = ((Sample.Volume+Solution)/Sample.Volume))%>%
  mutate(cal_LDH = LDH*Dilution_Factor)%>%
  mutate(cal_CK = CK*Dilution_Factor)%>%
  mutate(cal_Na = (Na-0.68)*Dilution_Factor)%>%
  mutate(cal_K = (K-0.025)*Dilution_Factor)%>%
  mutate(cal_Cl = (Cl-2.8)*Dilution_Factor)%>%
  drop_na(Sample)
main_df2$Time_Point <- as.factor(main_df2$Time_Point)

```{r}
boxplot(cal_Cl ~ Session + Time_Point, data = main_df2)
```

### 2022-08-26 Draft Plots.Rmd
added cleaned data sheet and plots

@@

@@

@@

@@

>>>>

### Lactate Dehydrogenase PLot 2
```{r}
LDH_SUM2<-main_df2%>%
  summarySE(measurevar = "cal_LDH", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
```

```{r}
LDH_SUM2$Session_f = factor(LDH_SUM2$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

LDH_SUM2$Speed_f = factor(LDH_SUM2$Speed, levels=c("SW", "FW"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SW", "FW")

LDH_SUM2$Time_Point_f = factor(LDH_SUM2$Time_Point, levels=c("1", "2", "3"))
Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("1", "2", "3")

LDH_PLOT_2 <- ggplot(LDH_SUM2, aes(x = Time_Point_f, y= cal_LDH))+
            geom_errorbar(aes(ymin = cal_LDH-se, ymax =cal_LDH+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

LDH_PLOT_2

```
```{r}
LDH_Grouping <- ggarrange(LDH_PLOT_1,LDH_PLOT_2,labels=c("A", "B"), ncol=2, nrow=1, common.legend = TRUE, legend = "bottom")

LDH_Grouping
```

```{r}
ggsave(plot=LDH_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//LDHgrouping_Draft(26-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)

@@

###CK_PLOT2
```{r}
CK_SUM2<-main_df2%>%
  summarySE(measurevar = "cal_CK", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
```

```{r}
CK_SUM2$Session_f = factor(CK_SUM2$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

CK_SUM2$Speed_f = factor(CK_SUM2$Speed, levels=c("SW", "FW"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SW", "FW")

CK_SUM2$Time_Point_f = factor(CK_SUM2$Time_Point, levels=c("1", "2", "3"))
Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("1", "2", "3")

CK_PLOT_2 <- ggplot(CK_SUM2, aes(x = Time_Point_f, y= cal_CK))+
            geom_errorbar(aes(ymin = cal_CK-se, ymax =cal_CK+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(22, 15, 21, 16))+
            theme_classic()+
            theme(legend.position="right", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Creatine Kinase (units/L) \n",breaks = c(100,125,150,175,200,225,250,275,300,325,350), limits = c(100,350))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))

CK_PLOT_2

```{r}
CK_Grouping <- ggarrange(CK_PLOT_1,CK_PLOT_2,labels=c("A", "B"), ncol=2, nrow=1, common.legend = TRUE, legend = "bottom")

CK_Grouping
```
```{r}
ggsave(plot=CK_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//CKgrouping_Draft(26-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)

@@

###Sodum PLot 2
```{r}
Na_SUM2<-main_df2%>%
  summarySE(measurevar = "cal_Na", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
```

```{r}
Na_SUM2$Session_f = factor(Na_SUM2$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

Na_SUM2$Speed_f = factor(Na_SUM2$Speed, levels=c("SW", "FW"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SW", "FW")

Na_SUM2$Time_Point_f = factor(Na_SUM2$Time_Point, levels=c("1", "2", "3"))
Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("1", "2", "3")

Na_PLOT_2 <- ggplot(Na_SUM2, aes(x = Time_Point_f, y= cal_Na))+
            geom_errorbar(aes(ymin = cal_Na-se, ymax =cal_Na+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

Na_PLOT_2

```{r}
NA_Grouping <- ggarrange(Na_PLOT_1,Na_PLOT_2,labels=c("A", "B"), ncol=2, nrow=1, common.legend = TRUE, legend = "bottom")

NA_Grouping
```

```{r}
ggsave(plot=NA_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Nagrouping_Draft(26-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)

@@

###Potassium Plot 2
```{r}
K_SUM2<-main_df2%>%
  summarySE(measurevar = "cal_K", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
```

```{r}
K_SUM2$Session_f = factor(K_SUM2$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

K_SUM2$Speed_f = factor(K_SUM2$Speed, levels=c("SW", "FW"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SW", "FW")

K_SUM2$Time_Point_f = factor(K_SUM2$Time_Point, levels=c("1", "2", "3"))
Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("1", "2", "3")

K_PLOT_2 <- ggplot(K_SUM2, aes(x = Time_Point_f, y= cal_K))+
            geom_errorbar(aes(ymin = cal_K-se, ymax =cal_K+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

K_PLOT_2

```{r}
K_Grouping <- ggarrange(K_PLOT_1,K_PLOT_2,labels=c("A", "B"), ncol=2, nrow=1, common.legend = TRUE, legend = "bottom")

K_Grouping
```

```{r}
ggsave(plot=K_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Kgrouping_Draft(26-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)

@@

###Chorine PLot 2
```{r}
Cl_SUM2<-main_df2%>%
  summarySE(measurevar = "cal_Cl", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
```

```{r}
Cl_SUM2$Session_f = factor(Cl_SUM2$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

Cl_SUM2$Speed_f = factor(Cl_SUM2$Speed, levels=c("SW", "FW"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SW", "FW")

Cl_SUM2$Time_Point_f = factor(Cl_SUM2$Time_Point, levels=c("1", "2", "3"))
Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("1", "2", "3")

Cl_PLOT_2 <- ggplot(Cl_SUM2, aes(x = Time_Point_f, y= cal_Cl))+
            geom_errorbar(aes(ymin = cal_Cl-se, ymax =cal_Cl+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

Cl_PLOT_2

```{r}
Cl_Grouping <- ggarrange(Cl_PLOT_1,Cl_PLOT_2,labels=c("A", "B"), ncol=2, nrow=1, common.legend = TRUE, legend = "bottom")

Cl_Grouping
```

```{r}
ggsave(plot=Cl_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Clgrouping_Draft(26-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
